\documentclass[11pt]{article}
% Use official ACL template if available (e.g., acl.sty)
% \usepackage{acl}
\usepackage[hyperfootnotes=false]{hyperref}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{url}
\renewcommand{\UrlFont}{\ttfamily\small}

\title{SWE-Mutation: A Code Mutation Framework for Software Engineering Tasks}

\author{
  Author Name\thanks{Add affiliation and funding information} \\
  Affiliation \\
  \texttt{email@example.com}
}

\date{}

\begin{document}
\maketitle

\begin{abstract}
We present SWE-Mutation, a framework for code mutation targeting software engineering tasks.
It provides lightweight AST-based mutation operators and supports batch mutation generation for Python files,
enabling data augmentation, robustness evaluation, and experiments aligned with the paper's methodology. We describe
the system design and implementation and provide example usage and experimental interfaces.
\end{abstract}

\section{Introduction}
Small code changes can affect semantics, executability, and performance in software engineering and program understanding tasks.
We generate controlled variants with mutation operators to analyze model sensitivity and generalization to different code forms.

\section{Related Work}
Briefly summarize mutation testing, program transformation, and data augmentation lines of work and representative methods.

\section{Method}
We implement three basic mutation operators:
\begin{itemize}
  \item Comparison flip (\texttt{flip-comparisons}): swap \texttt{>} with \texttt{<}, \texttt{>=} with \texttt{<=}, and \texttt{==} with \texttt{!=}.
  \item Negated conditions (\texttt{negate-ifs}): negate the conditions of \texttt{if} statements.
  \item Plus-minus swap (\texttt{swap-plus-minus}): swap \texttt{+} and \texttt{-} in binary operations.
\end{itemize}
Operators are implemented with Python AST, aiming to preserve syntactic correctness and compilability.

\section{System}
The system consists of:
\begin{itemize}
  \item \textbf{mutations}: core operators and AST transforms.
  \item \textbf{pipeline}: reads input files, applies operators, and writes outputs.
  \item \textbf{cli}: command-line interface for batch processing and integration.
\end{itemize}
Users can quickly generate data via \texttt{python -m swe\_mutation.cli generate}.

\section{Experimental Setup}
Describe data sources, evaluation tasks, metrics, and baselines. Compare performance under different mutation strengths and combinations.

\section{Results and Analysis}
Present tables and visualizations. Discuss the impact of operators and combinations, and statistical significance.

\section{Ethics Statement}
Clarify data/code sources and compliance, avoiding sensitive information and privacy leaks.

\section{Conclusion}
We release an extensible SWE-Mutation framework supporting convenient code-level mutation generation and experimental reproduction.
Future work includes richer semantics-preserving/changing operators, cross-language support, and a more complete evaluation suite.

\section*{Acknowledgements}
We thank collaborators and funding sources. We plan to open-source more operators and use cases to facilitate reproduction and comparison.

\bibliographystyle{acl_natbib}
\bibliography{refs}

\end{document}
